---
output: 
  stevetemplates::syllabus:
    latex_engine: xelatex
    #dev: cairo_pdf
geometry: margin=1in

title: "CJ 4310: Special Problems in the Criminal Justice System"
author: Seth Watts, PhD
date: "Fall 2025"

# coteaching: TRUE
email: "sbwatts@txstate.edu"
officehours: "Thurs 11-2 or by appt."
office: "Zoom"

web: "sethbwatts.com/courses"
classroom: "Zoom"
classhours: "Asynchronous"

fontfamily: mathpazo
fontsize: 11pt
header-includes:
   - \linespread{1.05}
   - \usepackage{xcolor}
   - \definecolor{txst}{HTML}{501214}
   
linkcolor: txst
urlcolor: txst
---
```{r setup, include=F}

library(knitr)
library(kableExtra)

```
# Overview

**Course Catalog Description**: This course is a study of contemporary problems in the administration, management, organization and operation of criminal justice agencies.

**Prerequisites**: CJ 2310 and CJ 2350 and CJ 2355 and CJ 2360 all with grades of "D" or better. Corequisite: CJ 3346 with a grade of "D" or better.

**Required Textbook**: [Mays, G. L., & Ruddell, R. (2019). Making sense of criminal justice: Policies and practices. Oxford University Press.](https://www.homeworkforyou.com/static_media/uploadedfiles/1714949674_779199__116..pdf) - No cost, PDF available.

**Additional Readings/ Resources**:

  - Required articles will be provided by the instructor in PDF format on Canvas.
  
  - Additional videos will be provided by the instructor on Canvas.
  
  - Access to reliable Internet, Canvas, and Microsoft Word/ some other word processing software.


**Course Rationale**: This class will broadly be centered around crime control strategies. The primary focus will be on how the Criminal Justice System attempts to control criminal activity. We will also cover how the community, environment, labor market, and technological innovations can be utilized to control crime. 

**Course Objectives**:

1. You'll learn this

2. And also that

3. Perhaps some of this too.

# Assignments and Evaluation

## Summary of Assignments

Below are the assignments and their points for the class:

```{r, echo=FALSE}
library(kableExtra)

assignments <- data.frame(
  Assignment = c("Discussion Questions (DQs)", "Paper Topic", "Paper Outline", "Final Paper", "Midterm Exam", "Final Exam", "Total"),
  Points = c("6.25 per (x12) = 75", "50", "75", "100", "100", "100 ", "500"),
  Percentage = c("15%", "10%", "15%", "20%", "20%", "20%", "100%")
)

kable(assignments, format = "latex", booktabs = TRUE, escape = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"), full_width = FALSE)


```
*Assigned Readings*: Unless otherwise specifically assigned, reading assignments are taken from the required
resources specified in this syllabus. The reading assignments listed for each class are those readings that a
student must complete before reviewing the corresponding module’s lecture or completing corresponding
module assignments. Not all of the assigned readings will be discussed in lectures; however, all assigned
readings may be covered on exams. See the course schedule for reading assignments.

*Discussion Questions*: Each week you will submit a question to me via Canvas. This question should be directed towards the readings for that week. For example let the following questions guide you in coming up with your questions that you will submit: What caught your eye in the readings? What are you not understanding? Are you curious about a certain policy's mechanics? How might a certain policy be perceived?

*Paper Topic*: In preparation for the paper outline and final paper, you will submit a paper topic to me via Canvas. Ideally this will be a short and sweet one sentence paper topic but can be two or three sentences. You can look ahead in the course readings to generate a paper topic. It is entirely up to you but must be within the confounds of the course topics. If it is a related topic but not covered in the class, let me know and we can discuss. 

*Paper Outline*: To help facilitate the development of your final paper, you will submit a paper outline via Canvas. This outline should be no more than three pages. It should include section and subsection headers, potential evidence to bring in, citations, and arguments to be made. It should serve as the scaffolding for your final paper. This is not a set in stone outline, if you deviate, you will not be penalized. However, if you change your paper topic after the outline is submitted, please notify me. Be sure to include a reference page (not included in the approximately 3 page limit). 

*Final Paper*: The final paper should be approximately 8-10 pages, with 5 different references from the class readings and 5 external references that were not covered in class. You should be using APA formatting for all of your writing assignments.^[See the following link for a guide to APA formatting: https://owl.purdue.edu/owl/research_and_citation/apa_style/apa_formatting_and_style_guide/index.html] Be sure to include a reference page (not included in the 8-10 page requirement). 

*Midterm Exam*:

*Final Exam*:

# Course Policies

**Calendar and Due Dates**: In addition to the information located in each week’s module in Canvas, a master calendar of due dates will be made available under the ‘Calendar’ section of the course homepage in Canvas. Should any adjustments be needed to original due dates, I will post an announcement to the ‘Announcements’ section and will adjust the calendar to reflect the modified timeline. This is NOT a self-paced or correspondence course.

**Late Work**: Written assignments are to be submitted by the due date by the times specified (Central
Time). In extreme cases, as approved by the instructor, late work will be accepted by an agreed upon
alternate due date. Work submitted late for other reasons will be penalized 10% for each day late.
Notify the instructor BEFORE an assignment is due if an urgent situation arises and the assignment will
not be submitted on time. Published assignment due dates are firm.

**Grade Records**: To the extent possible, I will try to make sure that grades for the assignments are posted
within approximately three days after its due date. On occasion, some assignments require intermediate feedback in which a longer turnaround should be expected. Once the assignment is evaluated, its grades will be placed into the Canvas gradebook and will be available to you. Exam/quiz grades will be posted upon completion of the exam/quiz. Individual reports will not be sent apart from the information recorded in Canvas, so you should periodically monitor the gradebook to assure your assignments have been received and graded.

**Academic Dishonesty**: All students taking classes in Criminal Justice must subscribe to the Texas State
University Honor Code (http://www.txstate.edu/honorcodecouncil/Academic-Integrity.html) and Code of
Student Conduct (http://www.dos.txstate.edu/handbook/rules/cosc.html). Failure to adhere to any
component of these documents may entail consequences ranging from serious (e.g. unexcused absences,
zero points assigned for exam grades, etc.) to severe (a course grade of “F” or even dismissal from the
University).

**Artificial Intelligence**: In this course, you are welcome and encouraged to use artificial intelligence platforms such as **ChatGPT** ONLY for pre-writing, brainstorming, and locating sources, unless otherwise specified in assignment instructions. You should not use AI to produce your own assignments or otherwise perform tasks that you are expected to be able to do or learn to do on your own. In short, ChatGPT isn’t taking this course; you are. You are here to learn, not to cut corners. Please take that responsibility seriously.

Your instructor will make every effort to be transparent in describing why you should complete each
assignment, what skills you will develop, and when/ how it is appropriate to use AI as a tool for completing the assignments.

**Avoiding Plagiarism**: Some students truly do not understand what plagiarism is, and therefore plagiarize
unwittingly or unintentionally. But ignorance is not an excuse for unethical academic conduct.

Moreover, read the following rules that apply regardless of the citation form or style you may be using.

1. *Direct Quotations* – Whenever you directly quote someone else, you must provide a citation to the
source of the material from which you are quoting. Moreover, you must put the material in
quotation marks or otherwise set it off in an indented quote so the reader knows what words are
yours and what words are quoted. It is unacceptable to use the words of others and only partially
quote the original source. This is true even if you provide citation to the source both in text and in
your references section!

1. *Paraphrasing/Indirect Quotations* – Whenever you indirectly quote someone else (i.e., you
paraphrase the work of another), you must provide a citation to the source of the material from
which you are paraphrasing. Simply changing the structure of a sentence, or a few words in a
sentence so that the sentence you write is not an exact quote from the original source does not
mean a citation is not needed. This is because the idea you are expressing is not your own, but
rather someone else’s.

1. *Using Other’s Ideas* – Even if you compose an entire paragraph of writing in your own words (i.e.,
neither quoted nor paraphrased), if the idea you are expressing in that paragraph is not your own, original idea, you must provide a citation to the source from which you obtained this idea.

1. *Collaborative Work* – If you collaborate on any work with someone else and fail to acknowledge
that collaboration, you are guilty of plagiarism. If you have received permission from you professor
to collaborate on some assignment, be sure that all of the contributor's names appear on the
submission.

1. *Altering or Revising Another’s Work* – If you alter or revise the work done by someone and submit
that work as your own, you have plagiarized. Similarly, if you allow someone else to alter or revise
work that you have done and then allow that person to submit it as his or her own work, you are
both guilty of plagiarism. Work that is not entirely your own must be credited by citation, both in
text and in your references page.

1. *Altering or Revising Your Own Prior Work* – You should also be aware that reusing or revising your
own work that was prepared for another class or another professor, and not bringing it to the
attention of the professor to whom you are submitting the revised work is also academic dishonesty.
If, for example, you have two classes that require a term paper, and you can write one paper that
meets the requirements of both classes, you may not submit that paper to both professors unless
you get permission to do so in advance from both professors. Similarly, if you wrote a paper several
semesters ago that can be revised and submitted in satisfaction of a paper requirement for a course
in which you are currently enrolled, doing so is academic dishonesty unless you get the advanced
permission of your professor to do so. The reason this is dishonest is that it is not an original work
prepared in satisfaction for the requirements on the course you are currently taking. Contact your
instructor for written approval if you are seeking an exception for unique cases.

**Canvas**: Along with this syllabus, all grades in this course will be posted to CANVAS. I will do my best to post the grades within a week of an exam. To access CANVAS, you can follow the following link:
https://canvas.txstate.edu. Should you need a laptop, the library loans them out to students. For more information, please contact the library or go to:
http://www.library.txstate.edu/about/departments/circ/laptop.

**Disability**: Students with a documented disability and/or those that believe they have a legitimate disability, are strongly encouraged to arrange a meeting with me to ensure they receive appropriate accommodations as set forth by the Office of Disabled Students. Students must contact the instructor within the first two weeks of the semester. If accommodations are needed, please contact the Office of Disabilities Services, as follows:

  - Office of Disability Services Suite 5-5.1, LBJ Student Center 601 University Drive San Marcos TX 78666 Phone: 512.245.3451 Fax: 512.245.3452 Office

  - Hours: Monday to Friday 8am -5pm Website: http://www.ods.txstate.edu/


# Course Schedule

```{r, echo=FALSE}
schedule <- data.frame(
  Week = 1:15,
  Date = c("Aug 25-31", "Sep 1-7", "Sep 8-14", "Sep 15-21", "Sep 22-28", "Sep 29-Oct 5", "Oct 6-12", "Oct 13-19", "Oct 20-26", "Oct 27-Nov 2", "Nov 3-9", "Nov 10-16", "Nov 17-23", "Nov 24-Dec 1", "Dec 2-9"),
  Topic = c("Politics and Policy", "Criminal Justice Policy", "Police I: Crime Control Agents", "Police II: Hot Spots & Problem Oriented Policing", "Police III: Focused Deterrence", "Courts, Prosecutors, & Sentencing", "Corrections: Prisons & Community Supervision",
            "Midterm", "Community-based I: CPTED", "Community-based II: Public Health Approach", "Technology & Surveilance", "Employment and Crime",
            "Evaluating What Works I", "Evaluating What Works II", "Final"),
  Readings = c("Syllabus; Textbook: Ch. 1, 2, & 3", "Welsh & Farrington (2011)", "Sherman (2011); Chalfin (2022)", "Braga et al. (2019), Hinkle et al. (2020); Reducing Crime Podcast Ep. #66 (David Weisburd)", "Braga et al. (2018); Reducing Crime Podcast Ep. #18 (Thomas Abt)", "Textbook: Ch. 7", "Textbook: Ch. 11, 12, & 13", "", "Welsh & Farrington (2008); Garvin, Cannuscio, & Branas (2013)", "Butts et al. (2015) Cure Violence", "Textbook: Ch. 15; Connealy et al. (2024), Piza et al. (2024)", "Heller (2014), Apel & Horney (2017)", "Sherman et al. (1997)", "TBD", "" ),  # Add readings
  Assignments = c("", "DQ 1", "DQ 2", "DQ 3", "DQ 4; Paper Topic due", "DQ 5", "DQ 6", "Midterm Exam", "DQ 7; Paper Outline due", "DQ 8", "DQ 9", "DQ 10", "DQ 11", "DQ 12; Final Paper due", "Final Exam"))

kable(schedule, format = "latex", booktabs = TRUE, longtable = FALSE, escape = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"), full_width = FALSE) %>%
  column_spec(3, width = "7cm") %>%  # Topic column
  column_spec(4, width = "7cm")      # Readings column

```

