---
output: 
  stevetemplates::syllabus:
    latex_engine: xelatex
    #dev: cairo_pdf
geometry: margin=1in

title: "CJ 4310: Special Problems in the Criminal Justice System"
author: Prof. Seth Watts
date: "Fall 2025"

# coteaching: TRUE
email: "sbwatts@txstate.edu"
officehours: "\\shrug - send me an email!"
office: "Zoom"

web: "sethbwatts.com/courses"
classroom: "Zoom"
classhours: "\\shrug"

fontfamily: mathpazo
fontsize: 11pt
header-includes:
   - \linespread{1.05}
   - \usepackage{xcolor}
   - \definecolor{txst}{HTML}{501214}
   
linkcolor: txst
urlcolor: txst
---
```{r setup, include=F}

library(knitr)
library(kableExtra)

```
# Course Description

This class will broadly be centered around crime control strategies. The primary focus will be on how the Criminal Justice System attempts to control criminal activity. We will also cover how the community, environment, labor market, and technology can be utilized to control crime. 

# Course Objectives

1. You'll learn this

2. And also that

3. Perhaps some of this too.

# Required Textbook

[Mays, G. L., & Ruddell, R. (2019). Making sense of criminal justice: Policies and practices. Oxford University Press.](https://www.homeworkforyou.com/static_media/uploadedfiles/1714949674_779199__116..pdf) - No cost, PDF available.

# Assignments and Evaluation

## Summary of Assignments

## Grading 

# Course Policies

# Technical Support

# Course Schedule

```{r, echo=FALSE}
schedule <- data.frame(
  Week = 1:15,
  Date = c("Aug 25-31", "Sep 1-7", "Sep 8-14", "Sep 15-21", "Sep 22-28", "Sep 29-Oct 5", "Oct 6-12", "Oct 13-19", "Oct 20-26", "Oct 27-Nov 2", "Nov 3-9", "Nov 10-16", "Nov 17-23", "Nov 24-Dec 1", "Dec 2-9"),
  Topic = c("Introduction & Overview", "The Criminal Justice System", "Police I: Crime Control Agents", "Police II: Hot Spots & Problem Oriented Policing", "Police III: Focused Deterrence", "Courts, Prosecutors, & Sentencing", "Corrections: Prisons & Community Supervision",
            "Midterm", "Community-based I: CPTED", "Community-based II: Public Health Approach", "Technology & Surveilance", "Employment and Crime",
            "Evaluating What Works I", "Evaluating What Works II", "Final"),
  Readings = c("Syllabus", "Textbook: Ch. 2 & 3", "NA", "Braga et al. (2019), Hinkle et al. (2020); Reducing Crime Podcast Ep. #66 (David Weisburd)", "Braga et al. (2018); Reducing Crime Podcast Ep. #18 (Thomas Abt)", "Textbook: Ch. 7", "Textbook: Ch. 11, 12, & 13", "NA", "Welsh & Farrington (2008); Garvin, Cannuscio, & Branas (2013)", "Butts et al. (2015) Cure Violence", "Textbook: Ch. 15; Connealy et al. (2024), Piza et al. (2024)", "Heller (2014) Summer jobs, Apel & Horney (2017)", "Sherman et al. (1998)", "TBD", "NA" ),  # Add readings
  Assignments = c("Discussion Board 1", "Discussion Board 2", "Discussion Board 3", "Discussion Board 4", "Discussion Board 5; Paper Topic due", "Discussion Board 6", "Discussion Board 7", "Midterm Exam", "Discussion Board 8; Paper Outline due", "Discussion Board 9", "Discussion Board 10", "Discussion Board 11", "Discussion Board 12", "Discussion Board 13; Final Paper due", "Final Exam"))

kable(schedule, format = "latex", booktabs = TRUE, longtable = FALSE, escape = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"), full_width = FALSE) %>%
  column_spec(3, width = "7cm") %>%  # Topic column
  column_spec(4, width = "7cm")      # Readings column

```

